Echoes of Economic Downturn: Investigating the Persistent Impact of the Great Recession on Birth Rates Among Young Americans

### 2024-02-14 outputs/paper/paper.qmd
fixed table, resolve merge conflict

// TODO: kable

@@

@tbl-display-raw-data presents the birth rates for various age groups and racial categories in the United States from the year 1980 to 1989. Moreover, the birth rates are typically expressed per every 1,000 women in the population.To further understand this table, Year represent the years from the selected year range. The next six columns are different age groups for women, which are 15 to 19 years, 20 to 24 years, 25 to 29 years, 30 to 34 years, 35 to 39 years, and 40 to 44 years. Moreover, the last three columns are ethnic groups that describes the birth rates among the white, black, and Hispanic populations. However, some data for these groups are not available except 1989.

>>>>

@@

@tbl-display-raw-data uses R[@kable] presents the birth rates for various age groups and racial categories in the United States from the year 1980 to 1989. Moreover, the birth rates are typically expressed per every 1,000 women in the population.To further understand this table, Year represent the years from the selected year range. The next six columns are different age groups for women, which are 15 to 19 years, 20 to 24 years, 25 to 29 years, 30 to 34 years, 35 to 39 years, and 40 to 44 years. Moreover, the last three columns are ethnic groups that describes the birth rates among the white, black, and Hispanic populations. However, some data for these groups are not available except 1989.

// Visualization of the data for intuition
